A meta-analysis of mental rotation ability in the first years of life

### 2022-05-05 code/analysis.Rmd
Add Egger test + funnel plot

## Evaluation of publication bias

By visual inspection of a funnel plot of standard errors and effect sizes we detected a slight asymmetry indicating a small publication bias (Fig. 3).
Publication bias was also suggested by the results of an Egger regression test indicating that the slope of a weighted linear regression of the effect sizes on the standard errors is significantly different from zero (t(57) = 3.37, p = 0.001).
Nevertheless, a jackknife leave-one-out analysis confirmed that the current results are robust to the effects of individual studies (see Supplementary Table 5).

>>>>

## Publication bias and certainty assessment

```{r, publication_bias, echo=TRUE}
# Classical Egger regression test
(egger <- regtest(x = dat$gi, sei = dat$sei, model = "lm", predictor = "sei"))
(egger_ci <- confint(egger$fit)["Xsei", ])
```

By visual inspection of a funnel plot of standard errors and effect sizes we detected a slight asymmetry indicating a small publication bias (Fig. 3). Publication bias was also suggested by the results of an Egger regression test indicating that the slope of a weighted linear regression of the effect sizes on the standard errors is significantly different from zero in a two-sided $t$-test, $b = `r coef(egger$fit)["Xsei"]`$, $t(`r egger$dfs`) = `r egger$zval`$, $p = `r print_p(egger$pval)`$, 95% confidence interval (CI) [`r egger_ci["2.5 %"]`, `r egger_ci["97.5 %"]`]. Nevertheless, a jackknife leave-one-out analysis confirmed that the current results are robust to the effects of individual studies (Supplementary Table 3).

```{r, fig3, include=TRUE, fig.height=3.5, fig.width=5.56, fig.cap="(ref:fig3-caption)", out.width="50%"}
# Compute funnel
funnel_z_crit <- stats::qnorm(0.975)
funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
funnel <- data.frame(
  x = c(
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
  ),
  y = c(funnel_max_se, 0, 0, funnel_max_se)
)

# Create funnel plot
dat %>%
  ggplot(aes(x = gi, y = sei)) +
  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
  # Meta-analytic effect size
  geom_vline(xintercept = summ_brm$intercept, color = "black") +
  # Experiment-specific effect sizes
  geom_point(shape = 0) +
  # Funnel
  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
  # Styling
  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
  scale_y_reverse() +
  coord_cartesian(
    xlim = c(-2.5, 2.5),
    ylim = c(funnel_max_se, 0),
    expand = FALSE
  ) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    y = "Standard error",
  ) +
  theme_classic() +
  theme(
    axis.line = element_line(colour = "black"),
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    text = element_text(family = "Helvetica", color = "black")
  )

# Save the plot
ggsave(here(figures_dir, "funnel.pdf"), width = 5.56, height = 3.5)
```

(ref:fig3-caption) **Evaluation of publication bias.** The funnel plot shows the standard errors and the effect sizes for each of the individual studies. The funnel contours (dashed lines) show a 95%-pseudo-confidence interval of the standard error around the meta-analytic effect size (vertical solid line). A slight asymmetry induced by the underrepresentation of studies with high standard error and small effect size suggest a small publication bias.
